---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
The raw data was originally archived in a zip format. Using the following R code the data archive is unzipped, loaded into the the environment, and the date variable transformed from the character class into the date class.
```{r Processing}
unzip("activity.zip")
Activity <- read.csv("activity.csv")
Activity$date <- as.Date(Activity$date)
summary(Activity)
```
## What is mean total number of steps taken per day?
```{r Mean per Day}
steps_per_day <- aggregate(steps ~ date, data=Activity, sum)
hist(steps_per_day$steps,xlab="Steps per Day", main = "Histogram of Steps per Day")
mean_steps <- mean(steps_per_day$steps)
median_steps <- median(steps_per_day$steps)
```
The arithmatic mean for the number of steps taken per day is `r mean_steps` and the median is `r median_steps`

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
