---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r, setup, echo=FALSE}
options(scipen=2, digits = 2)
```
## Loading and preprocessing the data

The raw data was originally archived in a zip format. Using the following R code the data archive is unzipped, loaded into the the environment, and the date variable transformed from the character class into the date class.

```{r Processing}
unzip("activity.zip")
Activity <- read.csv("activity.csv")
Activity$date <- as.Date(Activity$date)
summary(Activity)
```

## What is mean total number of steps taken per day?

```{r, Mean per Day}
steps_per_day <- aggregate(steps ~ date, data=Activity, sum)
hist(steps_per_day$steps,xlab="Steps per Day", main = "Histogram of Steps per Day")
mean_steps <- mean(steps_per_day$steps)
median_steps <- median(steps_per_day$steps)
```

The arithmatic mean for the number of steps taken per day is `r mean_steps` and the median is `r median_steps`.

## What is the average daily activity pattern?
```{r}
steps_per_interval <- aggregate(steps ~ interval, data=Activity, mean)
plot(steps_per_interval$interval, steps_per_interval$steps, type ="l", xlab = names(steps_per_interval)[1], ylab = names(steps_per_interval)[2])
max_int <- steps_per_interval$interval[which.max(steps_per_interval$steps)]
```
The 5 min interval with the highest average number of steps is `r max_int`. 

## Imputing missing values
We will determine how many missing values exist by using a sum function on Boolean objects where True equals 1 and False equals 0. Then we replace the *NA* values using the interval means.
```{r}
missing_values <- sum(is.na(Activity$steps))
New_Activity <- cbind(Activity,steps_per_interval$steps)
New_Activity$steps[is.na(New_Activity$steps)] <- New_Activity$`steps_per_interval$steps`[is.na(New_Activity$steps)]
New_Activity <-New_Activity[,1:3]
New_steps_per_day <- aggregate(steps ~ date, data=New_Activity, sum)
hist(New_steps_per_day$steps,xlab="Steps per Day", main = "Histogram of Steps per Day")
New_mean_steps <- mean(New_steps_per_day$steps)
New_median_steps <- median(New_steps_per_day$steps)
mean_diff <- mean_steps - New_mean_steps
median_diff <- median_steps - New_median_steps
```
After replacing the `r missing_values` missing values with the interval means, the mean number of steps taken per day is `r New_mean_steps` with a difference of `r mean_diff` from the previous mean showing no change. However, The median is now `r New_median_steps`, which a difference of `r median_diff` from the previous mean.

## Are there differences in activity patterns between weekdays and weekends?

